### 2018-09-20 FrascatiPlot/Paper/aps/main.tex
for journal submission: revised conclusions and outlook

A quantitative direct comparison of the two production scenarios has been proposed recently in \cite{Mrowczynski:2016xqm}, that resulted in the proposal to study the production rates of nuclei with similar mass but very different internal structure, in particular of \hefour~and ${}^{4}\mathrm{Li}$ \cite{Bazak:2018hgl}. However, as the ${}^{4}\mathrm{Li}$ is not stable with respect to strong decay, its measurement is experimentally very challenging and probably less constraining than the comparison with the hyper-nuclei proposed here.
We propose that \bA~is systematically measured in all collision systems by exploiting the large statistics sample that will be available with the LHC Run 3 \& 4, in order to rule out or support the aforementioned scenarios. 
%As a matter of fact, the upcoming years of LHC data taking provide a unique opportunity for the final understanding of (anti-)(hyper-)nuclei production.
%Setting a final word on the production mechanisms is not only in the interest of the heavy-ion community, but has a broader application in astrophysics and dark-matter searches, by representing an essential input for the measurement of (anti-)nuclei in space with ongoing \cite{Alcaraz:2000ss, Poulin:2018wzu} and future \cite{AMS100, Aramaki:2015laa} experiments. 
%In addition to this, the study of light(anti-)nuclei might serve as a baseline for understanding the debated nature of exotic states such as the X(3872), that has been interpreted as tetraquark state or hadronic molecule \cite{Esposito:2015fsa, Cho:2017dcy}.

@@

\section{Summary, conclusions, and outlook}
While it is often argued that the coalescence and the thermal model approach give very similar predictions for the production of light anti- and hyper-nuclei in heavy-ion collisions, the study presented here shows that large differences can be expected for hyper-nuclei with extended wave-functions. In the following, we summarise our main conclusions:
\begin{enumerate}
	\item For the production of $A=2$ and $A=3$ (anti-)nuclei in heavy-ion collisions, the thermal and coalescence models give similar predictions for a source volume that is constrained by experimental data on (anti-)deuteron production in central Pb--Pb collisions at the LHC.
	\item For the production of hyper-triton, the thermal and coalescence models give very different predictions as a function of source volume. In particular, the yield of hyper-triton appears to be suppressed by about two orders of magnitude in pp collisions with respect to the production of \hethree. The very limited amount of currently available data favours the thermal model prediction within our assumptions.
	\item Systematic measurements in pp, p--Pb, and Pb--Pb collisions at LHC energies have a unique potential to clarify the production mechanism and the nature of composite QCD objects. Ideally, such measurements are accompanied by systematic measurements of the HBT radii in the same multiplicity/centrality classes and collision systems.
\end{enumerate}

We would like to remark that our study is deliberately based on many simplified assumptions in order to allow for a completely analytical treatment of the problem. As mentioned earlier, future studies should be based on more realistic approximations (in particular the wave-function), which requires numerical calculations. 
Moreover, as the study presented here has been carried out for a specific value of transverse momentum per nucleon, it will be interesting to explore further the \pt~dependence of the observations made here in comparison to future and currently available data.

In a follow-up publication, we plan to extend our study to predictions for the $A=4$ systems introduced in Tab.~\ref{tab:nucleusradii} and to more exotic QCD objects like the X(3872). In fact, if the X(3872) corresponds to a loosely bound $\overline{D}^{*0}$--$D^{0}$ molecule, the rms of its wave-function can be as large as $4.9^{+13.4}_{-1.4}$~fm \cite{Artoisenet:2010uu}, which is very similar to that of the hyper-triton. Thus, its possible production via a coalescence mechanism in pp collisions would be subject to a similar suppression as the hyper-triton. Additional theoretical studies are encouraged in view of the high-luminosity phase of the LHC (Run 3 $\&$ 4), where $A = 4$ hyper-nuclei and other rare composite objects will become experimentally accessible.

>>>>

A quantitative direct comparison of the two production scenarios has been proposed recently in \cite{Mrowczynski:2016xqm}, that resulted in the proposal to study the production rates of nuclei with similar mass but very different internal structure, in particular of \hefour~and ${}^{4}\mathrm{Li}$ \cite{Bazak:2018hgl}. However, as the ${}^{4}\mathrm{Li}$ is not stable with respect to strong decay, its measurement is experimentally very challenging and probably less constraining than the comparison with the hyper-nuclei proposed here.
We propose that \bA~is systematically measured in all collision systems by exploiting the large statistics sample that will be available with the LHC Run 3 \& 4, in order to rule out or support the aforementioned scenarios.

@@

\section{Conclusions and outlook}
%While it is often argued that the coalescence and the thermal model approach give very similar predictions for the production of light anti- and hyper-nuclei in heavy-ion collisions, the study presented here shows that large differences can be expected for hyper-nuclei with extended wave-functions. In the following, we summarise our main conclusions:
We summarise our main conclusions as follows:
\begin{enumerate}
	\item For the production of $A=2$ and $A=3$ (anti-)nuclei in heavy-ion collisions, the thermal and coalescence models give similar predictions for a source volume that is constrained by experimental data on d, $\bar{\mathrm{d}}$~production in central Pb--Pb collisions at the LHC.
	\item For the production of hyper-triton, the thermal and coalescence models give very different predictions as a function of source volume. In particular, the yield of hyper-triton appears to be suppressed by about two orders of magnitude in pp collisions with respect to the production of \hethree. The very limited amount of currently available data favours the thermal model prediction within our assumptions.
	\item Systematic measurements in pp, p--Pb, and Pb--Pb collisions at LHC energies have a unique potential to clarify the production mechanism and the nature of composite QCD objects. Ideally, such measurements are accompanied by systematic measurements of the HBT radii in the same multiplicity/centrality classes and collision systems.
\end{enumerate}

%We would like to remark that our study is deliberately based on many simplified assumptions in order to allow for a completely analytical treatment of the problem. As mentioned earlier, future studies should be based on more realistic approximations (in particular the wave-function), which requires numerical calculations. 
%Moreover, as the study presented here has been carried out for a specific value of transverse momentum per nucleon, it will be interesting to explore further the \pt~dependence of the observations made here in comparison to future and currently available data.
As our study is deliberately based on simplified assumptions that allow for a completely analytical treatment of the problem, future studies should be based on more realistic approximations (in particular the wave-function), which require numerical calculations. Moreover, it will be interesting to explore further the \pt~dependence of the observations made here in comparison to future and currently available data.

In a follow-up publication, we plan to extend our study to predictions for the $A=4$ systems introduced in Tab.~\ref{tab:nucleusradii} and to more exotic QCD objects like the X(3872), which has been interpreted as tetraquark state or hadronic molecule \cite{Esposito:2015fsa, Cho:2017dcy}. 
In fact, if the X(3872) corresponds to a loosely bound $\overline{D}^{*0}$--$D^{0}$ molecule, the rms of its wave-function can be as large as $4.9^{+13.4}_{-1.4}$~fm \cite{Artoisenet:2010uu}, which is very similar to that of the hyper-triton. Thus, its possible production via a coalescence mechanism in pp collisions would be subject to a similar suppression as the hyper-triton. 
%Additional theoretical studies are encouraged in view of the high-luminosity phase of the LHC (Run 3 $\&$ 4), where $A = 4$ hyper-nuclei and other rare composite objects will become experimentally accessible.
The upcoming high-luminosity phase of the LHC (Run 3 $\&$ 4), where $A = 4$ hyper-nuclei and other rare composite objects will become experimentally accessible, will provide a unique opportunity for the final understanding of (anti-)(hyper-)nuclei production.
Setting a final word on the production mechanisms is not only in the interest of the heavy-ion community, but has a broader application in astrophysics and dark-matter searches, by representing an essential input for the measurement of (anti-)nuclei in space with ongoing \cite{Alcaraz:2000ss, Poulin:2018wzu} and future \cite{AMS100, Aramaki:2015laa} experiments. 
%In addition to this, the study of light(anti-)nuclei might serve as a baseline for understanding the debated nature of exotic states such as the X(3872), that has been interpreted as tetraquark state or hadronic molecule \cite{Esposito:2015fsa, Cho:2017dcy}.
